The Journey from Wild to Textbook Data: A Case Study from the National Longitudinal Survey of Youth

### 2021-09-16 paper/paper.Rmd
Edit feature plot.

The next step is that explore the mean hourly wage data. In this case, we only explore the wages data of up to $12^{th}$ grade. Table \ref{tab:summarytable} shows that the median of the overall wage of the cohort is only 7.2, while the mean is 11.87. It indicates that the data might contains a lot of extreme values.

```{r summarytable}
```

@@

However, we can not be sure only by observing the summary statistics. Hence, we use visualisation techniques to investigate this matter. Figure \ref{fig:feature-plot} conveys a problem in the mean hourly wage values. Figure \ref{fig:feature-plot} A shows that some observations have an exceptionally high figure of wages, even more than US$10,000 per hour. In Figure \ref{fig:feature-plot} B, we barely see any difference in the minimum, median, and maximum value of the wages since the distribution is heavily skewed to the right.

```{r feature-plot, fig.cap = "Several plots showing anomalies observed the input data. XX Add a couple more plots that reveal the initial problems in the data. Plot A portrays the pattern of mean hourly wage of high school cohort from 1979 to 2018 of each ID in US Dollar; Plot B shows the distribution of their minimum, median, and maximum value. We can see that some IDs had an extremely high of wages and it made the distribution of the three features is extremely skewed.", fig.width=6, fig.height=4}
```

In Figure \ref{fig:high-wages}, we plot some respondents with a high value of mean hourly wages. We filter all of the IDs who earned more than US$ 500 per hour on average. We find that these respondents only experienced one point of extremely high wages. Thus, we suspect that these high values are erroneous resulted from a data entry error.

```{r high-wages, fig.cap= "6 out of 45 IDs with extremely high mean hourly wage. Most of the IDs only have one point of high wage."}
```

Further, we take 36 samples randomly from the data and plot them, as shown in Figure \ref{fig:sample-plot}. It implies that not only that some observations earn extremely high figures of wages, but some also have reasonably fluctuated wages, for example, the IDs in panel numbers 5, 7, and 11. The plot also implies that the samples have a different pattern of mean hourly wages. Some have had flat wages for years but had a sudden increase in one particular year, then it gone down again, while the others experienced an upsurge in their wage, for instance, the IDs in panel 9.

>>>>

The next step is that explore the mean hourly wage data. In this case, we only explore the wages data of up to $12^{th}$ grade.  Here, we use visualisation techniques to do IDA.

@@

We take 36 samples randomly from the data and plot them, as shown in Figure \ref{fig:sample-plot}. It implies that these respondents have a lot of variability in wages, for example, the IDs in panel numbers 5, 7, and 11. The plot also implies that the samples have a different pattern of mean hourly wages. Some have had flat wages for years but had a sudden increase in one particular year, then it gone down again, while the others experienced an upsurge in their wage, for instance, the IDs in panel 9.

Further, we investigate the summary statistics of wages. 
Figure \ref{fig:feature-plot} conveys a problem in the mean hourly wage values. Figure \ref{fig:feature-plot} A shows that some observations have an exceptionally high figure of wages, even more than US$10,000 per hour. In Figure \ref{fig:feature-plot} B, we barely see any difference in the minimum, median, and maximum value of the wages since the distribution is heavily skewed to the right. The problem is more clearly conveyed in Figure \ref{fig:feature-plot} C where there is no extreme values in the minimum and median values of wages but the maximum values show some anomalies. In Figure \ref{fig:feature-plot} D, we show the example of anomaly in one observation. This respondent only experienced one point of extremely high wages. Thus, we suspect that these high values are erroneous resulted from a data entry error.

```{r summarytable, eval = FALSE}
```

```{r high-wages}
```

```{r feature-plot, fig.cap = "Several plots showing anomalies observed the input data. Plot A portrays the pattern of mean hourly wage of high school cohort from 1979 to 2018 of each ID in US Dollar. We can see some extremely high wages; Plot B shows the distribution of their minimum, median, and maximum value. We can also see that some IDs had an extremely high of wages and it made the distribution of the three features is extremely skewed; Plot C shows the extreme values more clearly; Plot D shows an ID with a suspected erronous wages.", out.width="90%"}
```
